Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-02 paper/ms.tex
update manuscript

\subsubsection{Not SB2}
We derived limits on blended spectroscopic companions using the
stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, the
spectra would have revealed companions with flux fractions $F_2/F_1
\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).

\subsubsection{RVs}
The radial velocities from FEROS, CHIRON, and Veloce can be used to
detect massive bound companions orbiting \tn.  We searched for the
presence of planetary and stellar-mass companions \replaced{using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits, and performed two sets of fits}{in two different regimes:
first, at the orbital period of the transiting object, and second, at
longer orbital periods to constrain the presence of a massive bound
companion. }.

@@

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
detected such a system.  Figure~\ref{fig:fpscenario} shows the
resulting limits; weakened sensitivity at harmonics of the baseline
occur at lower masses and smaller projected separations than shown on
the plot. The conversion from mass to brightness contrast was
performed using the same 35 Myr MIST isochrones and assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}

@@

The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends, and {\it iii)} the eclipses are
caused by neighboring stars outside $\approx 2''$.  The only scenario
not formally ruled out is a background eclipsing binary.  A simple
(fallacious) argument on the a priori probability of background blends
follows from counting statistics.  The local density of $T<15.1$ stars
around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
not excluded by the SOAR HRCam contrast curve, for a randomly selected
star we would expect $1.0\times10^{-4}$ potential $T<15.1$
contaminants, which appears small.

@@

\added{The second model, which used just the TESS data and the
cluster-isochrone stellar parameter priors,
formally yielded only a one-sided limit on the planet radius.  The
reason is that the $b$--$R_{\rm p}/R_\star$ degeneracy was not broken:
the combination of uncertain stellar parameters and
the grazing geometry allowed very
large planet-to-star radius ratios for very large impact parameters.
Based on our mass upper limit of $1.20\,M_{\rm Jup}$, we might argue
in favor of discarding the large-radius solution, since no sub-Jovian
mass objects are known to be larger than $\sim$$3R_{\rm Jup}$.  Had we
imposed this additional prior, then the TESS-only model would have
yielded
\begin{align}
  R_{\rm p} &= 0.836^{+0.208}_{-0.121} R_{\rm Jup} \\
  b &= 0.957^{+0.027}_{-0.017}.
\end{align}
Although these parameters are in 1-$\sigma$ agreement with our adopted
joint model of the TESS and ground-based data, we preferred the first
model both because it included all available data, and because it
succeeded in breaking the $b$--$R_{\rm p}/R_\star$ degeneracy without
requiring the adoption of informed priors.
}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf \tn\ compared to known transiting planets}.
    {\it Top}: Planet radii versus ages.  Systems younger than
    100$\,$Myr are emphasized.  Ages and radii are from the NASA
    Exoplanet Archive on 27 Aug 2020.  Precise ages are known for only
    a small fraction of the gray points.
    {\it Bottom}: Planet radii versus orbital periods. The known young
    transiting planets do not obviously overlap with the populations of
    known hot Jupiters or sub-Neptunes.
		\label{fig:population}
	}
	\vspace{-0.2cm}
\end{figure}

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - u_1 ( 1 - \mu ) - u_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, $u_i$ are the limb-darkening
parameters, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
  \label{eq:ephem}
\end{align}
% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex

>>>>

\subsubsection{Not SB2}
We derived limits on blended spectroscopic companions using the
stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, the
spectra would have revealed companions with flux fractions $F_2/F_1
\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
\added{The outer limit in projected separation for associated
companions is the distance at which the Keplerian orbital velocity is
well below the rotational broadening. This condition translates to a
projected separation of $10$--$20\,{\rm AU}$, depending on the
companion mass.  For chance alignments, the same restrictions on
velocity separation apply, but out to a projected separation equal to
the CHIRON slit width of $\approx 1''$.}

\subsubsection{RVs}
The radial velocities from FEROS, CHIRON, and Veloce can be used to
detect massive bound companions orbiting \tn.  We searched for
\deleted{the presence of }planetary and stellar-mass companions
\replaced{using \texttt{radvel} \citep{fulton_radvel_2018}.  We
assumed circular orbits, and performed two sets of fits.}{in two
different regimes: first, at the orbital period of the transiting
object, and second, at longer orbital periods to constrain the
presence of a massive bound companion.}

@@

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and drew their semi-amplitudes and periods from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
detected such a system.  Figure~\ref{fig:fpscenario} shows the
resulting limits; weakened sensitivity at harmonics of the baseline
occur at lower masses and smaller projected separations than shown on
the plot. The conversion from mass to brightness contrast was
performed using the same isochrone models and assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}

@@

The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends\added{\footnote{There is
a small gap in the upper panel of
Figure~\ref{fig:fpscenario}, corresponding to a $\approx 0.7 M_\odot$
companion HEB at a projected separation of $\approx$15$\,$AU. This
region of parameter space is, in our view, small enough to be safely
ignored.}}, and {\it iii)} the eclipses are caused by neighboring
stars outside $\approx 2''$.  The only scenario not formally ruled out
is a background eclipsing binary.  A simple, and fallacious, argument 
against background blends follows from counting
statistics.  The local density of $T<15.1$ stars around \tn, found by
counting from TIC8, is $3.7\times10^{-4} \,{\rm arcsec}^{-2}$.
Therefore within the relevant $\approx0.3''$ radius not excluded by
the SOAR HRCam contrast curve, for a randomly selected star we would
expect $1.0\times10^{-4}$ potential $T<15.1$ contaminants, which
appears small.

@@

\added{The second model, which used just the TESS data and the
cluster-isochrone stellar parameter priors,
formally yielded only a one-sided limit on the planet radius.  The
reason is that the $b$--$R_{\rm p}/R_\star$ degeneracy was not broken:
the combination of uncertain stellar parameters and
the grazing geometry allowed very
large planet-to-star radius ratios for very large impact parameters.
Based on our mass upper limit of $1.20\,M_{\rm Jup}$, we might argue
in favor of discarding the large-radius solution, since no sub-Jovian
mass objects larger than $\sim$$3R_{\rm Jup}$ are known to exist.  Had
we imposed this additional prior, then the TESS-only model would have
yielded
\begin{align}
  R_{\rm p} &= 0.836^{+0.208}_{-0.121} R_{\rm Jup} \\
  b &= 0.957^{+0.027}_{-0.017}.
\end{align}
Although these parameters are in 1-$\sigma$ agreement with our adopted
joint model of the TESS and ground-based data, we preferred the first
model both because it included all available data, and because it
succeeded in breaking the $b$--$R_{\rm p}/R_\star$ degeneracy without
requiring the adoption of informed priors.
}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf \tn\ compared to known transiting planets}.
    {\it Top}: Planet radii versus ages.  Systems younger than
    100 Myr are emphasized.  Ages and radii are from the NASA
    Exoplanet Archive on 27 Aug 2020.  Precise ages are known for only
    a small fraction of the gray points.
    {\it Bottom}: Planet radii versus orbital periods. The youngest
    known transiting planets do not obviously overlap with the
    populations of known hot Jupiters or sub-Neptunes.
		\label{fig:population}
	}
	\vspace{-0.2cm}
\end{figure}

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - u_1 ( 1 - \mu ) - u_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, $u_i$ are the limb-darkening
parameters, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272527 \pm 0.000593 \nonumber \\
  P\ [{\rm d}] &= 8.3248762 \pm 0.0000157 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.96 \pm 0.04.
  \label{eq:ephem}
\end{align}
% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex
